\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[top=1.5cm, left=1.5cm, right=1.5cm, bottom=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{tikz}

\title{Pascal's Triangle}
\author{Eason Shao}
\date{24/05/2024}

\begin{document}

    \maketitle

    Try and give combinatorial explanations of the identities where possible, as well as from algebraic methods (including definition, binomial expansion and generating functions).\bigskip

    Please experiment with the identities using small examples.

    \begin{enumerate}
        \item Find and prove the formula for \(^nC_k\), often also denoted as \(\binom{n}{k}\), which stands for the number of choosing \(k\) from \(n\) distinct objects. This is called the \textbf{Choose Coefficient} or the \textbf{Binomial Coefficient}.
        \item Write down the values of \(\binom{n}{k}\) where \(0 \leq k \leq n \leq 5\). What pattern did you spot, about the relationship between \(\binom{n}{k}\) and \(\binom{n-1}{k-1}\) and \(\binom{n-1}{k}\)
        \item Prove the \textbf{Pascal's Identity}, which is the pattern spotted above.
        \item Find and explain the values of \(\binom{n}{0}\) and \(\binom{n}{n}\).
        \item Prove the following symmetry of the binomial coefficients
        \[
            \binom{n}{k} = \binom{n}{n-k}.
        \]
        \item Find \(11^n\) where \(0 \leq n \leq 4\). What pattern did you spot? Does it hold for \(n \geq 5\)? Why?
        \item Write down the expansion of \((a+b)^n\), where \(a, b\) are arbitary real constants, and \(0 \leq n \leq 5\). What pattern did you spot between the coefficients of each term and the entries in Pascal's Triangle?
        \item Prove the \textbf{Binomial Expansion}, which is the pattern spotted above.
        \item Find a formula and prove for the following sum:
        \[
            \sum_{t = 0}^{n} \binom{n}{t}.
        \]
        \item Find a formula and prove for the following sum:
        \[
            \sum_{t = 0}^{n} t \binom{n}{t}.
        \]
        \item Prove the following identity:
        \[
            \sum_{t = 0}^{n} (-1)^t \binom{n}{t} = 0,
        \]
        i.e. the odd indexed terms in a row of Pascal's Triangle sum up to the even indexed terms.
        \item Prove the following identity:
        \[
            \sum_{t = k}^{n} \binom{n}{t} \binom{t}{k} = 2^{n - k} \binom{n}{k}.
        \]
        \item Prove the following identity:
        \[
            \sum_{t = 0}^{n} \binom{n}{t}^2 = \binom{2n}{n}.
        \]
        \item Prove the \textbf{Hockey-Stick Identity}, stated as follows:
        \[
            \sum_{t = m}^{n} \binom{t}{m} = \binom{n + 1}{m+1}.
        \]
        \item Prove the \textbf{Chu-Vandermonde Identity}, stated as follows:
        \[
            \sum_{t = 0}^{k} \binom{m}{t}\binom{n-m}{k-t} = \binom{n}{k}.
        \]

    \end{enumerate}
\end{document}